### 2019-11-06 paper_lap/03bvp.tex
updates

 \section{Boundary integral equations}
A classical way of solving the interior and exterior Dirchlet and Neumann Laplace and Helmholtz boundary value problems given above is to convert them to boundary integral equations. Before describing this reduction we first define the single and double layer potential operators and summarize their relevant properties.
 \subsection{Layer potentials}
\begin{definition}
Given a density $\sigma$ defined on $\Gamma$ the single-layer potential is defined by
\beqn
\cS_{\omega}[\sigma](\by) =  \int_{\Gamma} G_{\omega} (\bx,\by)\sigma(\bx) dS_{\bx} \, ,
\eeqn
where
\beqn
G_{\omega}(\bx,\by) = \begin{cases} 
\frac{i}{4} H_{0}(\omega |\bx-\by|) &\quad \omega \neq 0 \,, \\
-\frac{1}{2\pi} \log{|\bx-\by|} &\quad \omega = 0.
\end{cases}
\eeqn
Here $H_{0}$ is the Hankel 
function of the first kind of order $0$. 
Similarly, the double-layer potential is defined via the formula
\beqn
\cD_{\omega}[\sigma](\by) =\int_{\Gamma} \bnu(\bx) \cdot \nabla_{\bx} G_{\omega}(\bx,\by) \sigma(\bx) dS_{\bx},
\eeqn
where with some abuse of notation we denote the normal to $\Gamma$ at $\bx$ by $\bnu(\bx).$
\end{definition}
\begin{remark}
The layer potentials $\cS_{0}[\sigma]$ and $\cD_{0}[\omega]$ are the layer potentials for Laplace's equation.
\end{remark}
\begin{definition}
For $\bx \in \Gamma$ we define the kernel $K_{\omega}(\bx,\by)$ by
\begin{equation}
K_{\omega}(\bx,\by) =\bnu(\bx) \cdot \nabla_{\bx} G_{\omega}(\bx,\by),
\end{equation}
where $\nu(\bx)$ is the normal to $\Gamma$ at $\bx.$ It is often convenient to work instead with the parametrization of $K_{\omega}$ which we will denote by $k_{\omega}:[0,L]\times k[0,L] \to \mathbb{R}$ and is defined by
\begin{align}
k_{\omega}(s,t) = K_{\omega}(\gamma(s),\gamma(t)).
\end{align}
\end{definition}

The following theorems describe the behaviour of the single and double layer potentials in the vicinity of the boundary curve $\Gamma.$

\begin{theorem}\label{thm:potlim}
Suppose the point $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the inside along a path such that 
\begin{align}
-1+\alpha<\frac{\bx-\bx_0}{\|\bx-\bx_0\|} \cdot \gamma'(t_0) <1-\alpha
\end{align}
for some $\alpha >0.$ Then 
\begin{align}
&\lim_{\bx \to \bx_0} \cS_{\omega}[\sigma](\bx) = \cS_{\omega}[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD_{\omega}[\rho](\bx) = \cD_{\omega}[\rho](\bx_0)- \rho(\bx_0)\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS_{\omega}[\rho](\bx+\tau \bnu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS_{\omega}[\rho](\bx_0+\tau \bnu(t_0))+ \rho(\bx_0).
\end{align}
Similarly, if $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the outside then
\begin{align}
&\lim_{\bx \to \bx_0} \cS_{\omega}[\sigma](\bx) = \cS_{\omega}[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD_{\omega}[\rho](\bx) = \cD_{\omega}[\rho](\bx_0)+ \rho(\bx_0)\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS_{\omega}[\rho](\bx+\tau \bnu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS_{\omega}[\rho](\bx_0+\tau \bnu(t_0))- \rho(\bx_0).
\end{align}
\end{theorem}

We define the following operator which arises in the study of Neumann boundary value problems.
\begin{definition}
Let $\cS_{\omega}$ be the single-layer potential operator. Let $\bnu\cdot \nabla \cS_{\omega}$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\by \in \Gamma,$
\begin{align}
\bnu(\by)\cdot \nabla \cS_{\omega}[\rho] (\by) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS_{\omega}[\rho](\by + \tau \bnu(t_0)),
\end{align}
where $\gamma(t_0) = \by.$
\end{definition}

The following proposition relates the normal derivative of the single-layer operator to the double-layer operator. Its proof follows directly from the definitions.
\begin{proposition}
Let $\cS_{\omega},\cD_{\omega}:L^2(\Gamma) \to L^2(\Gamma)$ be defined as above. Let $\bnu \cdot \nabla \cS_{\omega}$ denote the normal derivative of $\cS_{\omega}$ in the sense of the previous definition. Then $\bnu \cdot \nabla \cS _{\omega}= \cD_{\omega}^{T}$ where $T$ denotes the adjoint operator with respect to the inner product
\beqn
< f,g > = \int_{0}^{L} f(\gamma(t)) g(\gamma(t)) dt\,.
\eeqn
In particular, for all $\rho,\sigma \in L^2(\Gamma)$
\begin{align}
\cD_{\omega}[\sigma](\gamma(t)] = \int_0^L k_{\omega}(s,t)\,\sigma(\gamma(s))\, {\rm d}s
\end{align}
and
\begin{align}
\bnu(\gamma(t))\cdot \nabla\cS_{\omega}[\rho](\gamma(t)] = \int_0^L k_{\omega}(t,s)\,\rho(\gamma(s))\, {\rm d}s.
\end{align}
\end{proposition}

@@

\begin{theorem} [Interior Dirichlet problem for the Laplace and Helmholtz equations]
Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. If $\omega$ is not an Dirichlet resonance of $\Omega$, then 
there exists a unique $\sigma \in L^{2}[0,L]$ which satisfies
\begin{align}
f(s)= - \sigma(s)+ \int_0^L k_{\omega}(t,s)\,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
Moreover, the solution to the interior Dirichlet problem for Laplace/Helmeholtz equation with boundary data $f$ is given by $u(\by) = \cD_{\omega}[\sigma](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem} [Exterior Dirichlet problem for the Laplace equation]
Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. Then there exists a unique $\sigma \in L^{2}[0,L]$ which
satisfies
\begin{align}
f(s)=  \sigma(s)+ \int_0^L (k_{0}(t,s) + 1)\,\sigma(t)\,{\rm d}t,
\end{align}
for all $s \in [0,L].$ 
Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD_{0}[\sigma](\by) + \int_{0}^{L} \sigma(t) dt$
for all $\by \in \mathbb{R}^2 \setminus \Omega.$
\end{theorem}

\begin{theorem} [Exterior Dirichlet problem for the Helmholtz equation]
Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. Suppose $\omega$ is not an interior Neumann resonance of $\Omega$. Then there exists a unique $\sigma \in L^{2}[0,L]$ which
satisfies
\begin{align}
f(s)=  \sigma(s)+ \int_0^L k_{\omega}(t,s) \,\sigma(t)\,{\rm d}t,
\end{align}
for all $s \in [0,L].$ 
Moreover, the solution to the exterior Dirichlet problem for Helmholtz's equation with boundary data $f$ is given by $u(\by) = \cD_{\omega}[\sigma](\by)$
for all $\by \in \mathbb{R}^2 \setminus \Omega.$
\end{theorem}

\begin{theorem}[Interior Neumann problem for the Laplace equation]
Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$ and satisfy $\int_{0}^{L} f(t) = 0$ \, .
Then there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
\begin{align}
f(s)=  \rho(s)+ \int_0^L (k_{0}(s,t) + 1)\,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
Moreover, the solution to the interior Neumann problem for Laplace equation with boundary data $f$ is given by $u(\by) = \cS_{0}[\rho](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem}[Interior Neumann problem for the Helmholtz equation]
Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. Suppose that $\omega$ is not an interior Neumann resonance for 
$\Omega$. 
Then there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
\begin{align}
f(s)=  \rho(s)+ \int_0^L k_{\omega}(s,t) \,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
Moreover, the solution to the interior Neumann problem for the Helmholtz equation with boundary data $f$ is given by $u(\by) = \cS_{\omega}[\rho](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem}[Exterior Neumann problem for the Laplace and Helmholtz equations]
Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. Suppose that $\omega$ is not an interior Dirichlet resonance for 
$\Omega$. 
Then there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
\begin{align}
f(s)=  \rho(s)+ \int_0^L k_{\omega}(s,t) \,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
Moreover, the solution to the interior Neumann problem for the Laplace ($\omega =0$) and Helmholtz equation with boundary data $f$ is given by $u(\by) = \cS_{\omega}[\rho](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{remark}
Even though the exterior Dirichlet and Neumann problems for Helmholtz equations are well-posed partial differential equations, the corresponding integral equations obtained by setting $u = \cD_{\omega}[\sigma](\by)$ for the Dirichlet problem and
$u = \cS_{\omega}[\rho](\by)$ are known to have a countable set of spurious resonances at the interior Neumann and Dirichlet resonances respectively. These spurious resonances can be eliminated by using a combined field integral representation 
for $u$ instead. We defer the extension of our method to the combined field representation to section (ENTER section number here).
\end{remark}

@@

The following Corollary characterizes of the solutions to the Dirichlet and Neumann boundary integral equations in the vicinity of a corner.

>>>>

 \section{Boundary integral equations}
A classical technique for solving the four Laplace boundary value problems given above is to reduce them to boundary integral equations. Before describing this procedure we first define the single and double layer potential operators and summarize their relevant properties.
 \subsection{Layer potentials}
\begin{definition}\label{def_layerpots}
Given a density $\sigma:\Gamma \to \mathbb{R}$ the single-layer potential is defined by
\beqn
\cS[\sigma](\by) =  \int_{\Gamma} G (\bx,\by)\sigma(\bx) {\rm d}S_{\bx} \, ,
\eeqn
where
\beqn
G(\bx,\by) = -\frac{1}{2\pi} \log{|\bx-\by|}.
\eeqn
Similarly, the double-layer potential is defined via the formula
\beqn
\cD[\sigma](\by) =\int_{\Gamma} \bnu(\bx) \cdot \nabla_{\bx} G(\bx,\by) \sigma(\bx) {\rm d}S_{\bx}.
\eeqn
\end{definition}

\begin{definition}
For $\bx \in \Gamma$ we define the kernel $K(\bx,\by)$ by
\begin{equation}
K(\bx,\by) =\bnu(\bx) \cdot \nabla_{\bx} G(\bx,\by),
\end{equation}
where $\nu(\bx)$ is the inward-pointing normal to $\Gamma$ at $\bx.$ It will often be convenient to 
work instead with a parametrization of $K.$ In particular, if $\gamma :[0,L] \to \Gamma$ is a counterclockwise 
arclength parametrization of $\Gamma,$ 
we denote by $k:[0,L]\times [0,L] \to \mathbb{R}$ the function defined by
\begin{align}
k(s,t) = K(\gamma(s),\gamma(t)).
\end{align}
\end{definition}

The following theorems describe the behavior of the single and double layer potentials in the vicinity of the boundary curve $\Gamma.$

\begin{theorem}\label{thm:potlim}
Suppose the point $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the inside along a path such that 
\begin{align}
-1+\alpha<\frac{\bx-\bx_0}{\|\bx-\bx_0\|} \cdot \gamma'(t_0) <1-\alpha
\end{align}
for some $\alpha >0.$ Then 
\begin{align}
&\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD[\rho](\bx) = \cD[\rho](\bx_0)- \rho(\bx_0)\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \bnu(\bx_0))+ \rho(\bx_0).
\end{align}
Similarly, if $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the outside then
\begin{align}
&\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD[\rho](\bx) = \cD[\rho](\bx_0)+ \rho(\bx_0)\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \bnu(\bx_0))- \rho(\bx_0).
\end{align}
\end{theorem}

We define the following operator which arises in the study of Neumann boundary value problems.
\begin{definition}\label{def_singder}
Let $\cS$ be the single-layer potential operator and $\bnu\cdot \nabla \cS$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\bx_0 \in \Gamma,$
\begin{align}
\bnu(\by)\cdot \nabla \cS[\rho] (\bx_0) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS[\rho](\bx_0 + \tau \bnu(\bx_0)),
\end{align}
where $\gamma(t_0) = \bx_0.$
\end{definition}

The following proposition relates the normal derivative of the single-layer operator to the double-layer operator. Its proof follows directly from Definitions \ref{def_layerpots} and \ref{def_singder}.
\begin{proposition}
Let $\cS,\cD:L^2(\Gamma) \to L^2(\Gamma)$ be defined as above. Let $\bnu \cdot \nabla \cS$ denote the normal derivative of $\cS$ in the sense of the previous definition. Then $\bnu \cdot \nabla \cS= \cD^{T}$ where $T$ denotes the adjoint operator with respect to the inner product
\beqn
\langle f,g \rangle = \int_{0}^{L} f(\gamma(t)) g(\gamma(t)) {\rm d}t\,,
\eeqn
where $\gamma:[0,L] \to \Gamma$ is a counterclockwise arclength parametrization of $\Gamma.$ 
In particular, for all $\rho,\sigma \in L^2(\Gamma),$
\begin{align}
\cD[\sigma](\gamma(t)) = \int_0^L k(s,t)\,\sigma(\gamma(s))\, {\rm d}s
\end{align}
and
\begin{align}
\bnu(\gamma(t))\cdot \nabla\cS[\rho](\gamma(t)) = \int_0^L k(t,s)\,\rho(\gamma(s))\, {\rm d}s.
\end{align}
\end{proposition}

@@

\begin{theorem} [Interior Dirichlet problem for Laplace's equation]
For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}[0,L],$ there exists a unique $\sigma \in L^{2}[0,L]$ which satisfies
\begin{align}
f(s)= - \sigma(s)+ \int_0^L k(t,s)\,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
Moreover, the solution to the interior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD_{\omega}[\sigma](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem} [Exterior Dirichlet problem for Laplace's equation]
For every $f:[0,L] \rightarrow \mathbb{R}$ in $L^{2}[0,L]$ there exists a unique $\sigma \in L^{2}[0,L]$ which
satisfies
\begin{align}
f(s)=  \sigma(s)+ \int_0^L (k(t,s) + 1)\,\sigma(t)\,{\rm d}t,
\end{align}
for all $s \in [0,L].$ 
Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD_{0}[\sigma](\by) + \int_{0}^{L} \sigma(t) dt$
for all $\by \in \mathbb{R}^2 \setminus \Omega.$
\end{theorem}

\begin{theorem}[Interior Neumann problem for Laplace's equation]
For every  $f:[0,L] \rightarrow \mathbb{C}$ in $L^{2}[0,L]$ such that $\int_{0}^{L} f(t) = 0,$ \, there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
\begin{align}
f(s)=  \rho(s)+ \int_0^L (k(s,t) + 1)\,\sigma(t)\,{\rm d}t,
\label{bie_intn}
\end{align}
Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS_{0}[\rho](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem}[Exterior Neumann problem for Laplace's equation]
For every $f:[0,L] \rightarrow \mathbb{C}$ in $L^{2}[0,L]$ there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
\begin{align}
f(s)=  \rho(s)+ \int_0^L k_{\omega}(s,t) \,\sigma(t)\,{\rm d}t,
\label{bie_extn}
\end{align}
Moreover, the solution to the interior Neumann problem for Laplace'sequation with boundary data $f$ is given by $u(\by) = \cS_{\omega}[\rho](\by)$ for all $\by \in \Omega.$
\end{theorem}

@@

The following Corollary, proved in \cite{serkhacha} gives a characterization of the solutions to the Dirichlet and Neumann boundary integral equations in the vicinity of a corner.

### 2019-11-06 paper_lap/04nprelim.tex
updates

\section{Numerical preliminaries}
In this section we summarize the numerical tools which are necessary for the main result. In particular we summarize the method for discretizing the boundary integral equation for the Dirichlet problem described in \cite{}, which uses the expansion in Theorem \ref{thm_cord}.
\subsection{Discretization of the Dirichlet problem}
In this section we sketch an algorithm for solving the interior Dirichlet boundary integral equation using a Nystr\"{o}m method; the exterior Dirichlet boundary integral equation can be discretized in a similar way. See \cite{} for a thorough description of the method. We begin by constructing a discretization of the boundary $\Gamma$ with nodes $s_1,\dots,s_N,$ and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
\begin{align}
f(t) = -\sigma(t) + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
\end{align}
with precision $\epsilon.$ We proceed by enforcing equality at the discretization nodes, which yields the system of equations
\begin{align}
f(s_i) \sqrt{w_i} = -\pi \sigma(s_i)\sqrt{w_i} +  \sqrt{w_i}\int_0^L K(\gamma(s_i),\gamma(t))\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
\end{align}
Scaling by the square root of the weights is equivalent to solving the problem in the $L^2$ sense, and results in discretized operators with condition numbers which are close to those of the original physical systems \cite{bremer3}.

The boundary $\Gamma$ is separated into intervals which are at least some distance $\delta$  (measured in terms of arclength) away from a corner and intervals of length $2 \delta$ centered about each corner. The former are discretized using a standard smooth quadrature rule such as nested Gauss-Legendre quadrature while the latter are discretized using a custom set of interpolation nodes constructed in the following way.

First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,40],$ $x \in [0,1]$ are discretized using nested Gauss-Legendre panels in $x$ and a single Gauss-Legendre panel in $\mu$. This creates a $N \times M$ matrix where $N$ denotes the number of spatial discretization points $r_i$ and $M$ denotes the number of $\mu_j$ chosen. $M$ and $N$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1/2]$ for any $\mu$ in the specified range. A singular value decomposition is then performed on the $N\times M$ matrix. Let $K$ denote the number of singular values greater than $\epsilon.$ The right singular vectors correspond to discretizations of an orthonormal set of functions $\phi_1,\dots,\phi_K$ such that $x^\mu$ is in the span of $\phi_1,\dots,\phi_K$ to within an accuracy of $\epsilon.$

Finally, a set of interpolation points $x_j,$ $j=1,\dots,K$ and quadrature weights $w_j,$ $j=1,\dots,K$ are chosen for $\phi_1,\dots,\phi_K$ such that the matrix $U_{ij} = \phi_i(x_j) \sqrt{x_j}$ is well-conditioned. In practice suitable interpolation points can be obtained by using the roots of $\phi_{K+1}$ and calculating the corresponding weights by solving a linear system. The corresponding discretization nodes and weights for the corner-containing intervals of $\Gamma$ are obtained by suitable translations and scalings of $\{x_j\}$ and $\{w_j\}.$

Once the discretization has been constructed it is necessary to construct appropriate quadrature for the integrals appearing in equation (\ref{eqn_1std}). When $s_i$ and $t$ do not belong to the same corner panel (in particular when either is not itself contained in a corner panel) then the weights and nodes associated with the discretization can be used as the quadrature rule. When $s_i$ corresponds to a corner panel special care must be taken. Instead, using an algorithm for generating generalized Gaussian quadratures \cite{}, quadrature nodes are chosen which integrate
\begin{align}
\int_{0}^\delta k(t,s_j) \tilde{\phi}_j(t)\,{\rm d}t
\end{align} 
where for ease of exposition we assume that the corner panel corresponds to $(-\delta,\delta)$ in the parametrization with $t=0$ corresponding to the corner itself. Moreover, it is assumed that $s_j$ lies in the half of a corner panel parametrized by $(-\delta,0)$ and $\tilde{\phi}_j$ is a suitably scaled and translated copy of the singular function obtained in the discretization step.
\begin{remark1}
Due to scale invariance, it suffices to compute quadratures for 
\begin{align}
\int_{0}^\frac{1}{2} k(t,-x_j) {\phi}_j(t)\,{\rm d}t,
\end{align} 
where $x_j$ was one of the original discretization nodes generated on the interval $[0,1/2].$
\end{remark1}
\begin{remark1}
By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{w}_{i,j}$ such that if $s_1,\dots,s_{2K}$ correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
\begin{align}
\left| \int_{-\delta}^\delta k(t,s_i) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{w}_{ij} \tilde{\phi}_{m}(t_j) \right| < \epsilon
\end{align}
for all $i=1,\dots,2K$ and $m=1,\dots,K.$
\end{remark1}

@@

\subsection{Discretization of the Neumann problem}
In principle a similar method could be employed to discretize the Neumann boundary integral equations. Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range $(-1/2,0)$) makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles. When the above method is run on these problems, discretization nodes tend to accumulate close to the corner (within $10^{-14}$). Apart from posing certain numerical challenges, it also makes the task of finding suitable quadrature formulae difficult. Instead a different set of discretization nodes and a different set of quadrature nodes must be constructed for each angle, drastically increasing the precomputation cost.

>>>>

\section{Numerical preliminaries}
In this section we summarize the numerical tools which are necessary for the main result. In particular we summarize the method for discretizing the boundary integral equation for the Dirichlet problem described in \cite{}, which uses the expansion in Theorem \ref{thm_cord}.
\subsection{Discretization of the Dirichlet problem}\label{sec:disc_dir}
In this section we sketch an algorithm for solving the interior Dirichlet boundary integral equation using a Nystr\"{o}m method; the exterior Dirichlet boundary integral equation can be discretized in a similar way. See \cite{} for a thorough description of the method.

The Nystr\"{o}m method proceeds as follows. We begin by constructing a discretization of the boundary $\Gamma$ with nodes $s_1,\dots,s_N,$ and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
\begin{align}\label{eqn:numpreint}
f(t) = -\sigma(t) + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
\end{align}
with precision $\epsilon.$ Once these nodes and weights have been generated we proceed by enforcing equality of (\ref{eqn:numpreint}) at the discretization nodes, which yields the system of equations
\begin{align}
f(s_i) \sqrt{w_i} = -\pi \sigma(s_i)\sqrt{w_i} +  \sqrt{w_i}\int_0^L K(\gamma(s_i),\gamma(t))\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
\end{align}
We note that scaling by the square root of the weights in the above equation is equivalent to solving the problem in the $L^2$ sense, and results in discretized operators with condition numbers which are close to those of the original physical systems \cite{bremer3}. The new unknowns are $\sigma_i = \sigma(s_i) \sqrt{w_i},$ $i=1,\dots,N.$ Next, for each interpolation node $s_i$ we find a collection of weights $W_{ij}$ such that
\begin{align}
\left|\int_0^L K(\gamma(s_i),\gamma(t))\, \sigma(t)\,{\rm d}t- \sum_{j=1}^N W_{ij} \sigma_j\, \sqrt{w_j} \right| < \epsilon,
\end{align}
resulting in the linear system
\begin{align}
  -\pi \sigma_i +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f(s_i) \sqrt{w_i},\quad i,j=1,\dots,N. 
\end{align}

%{\color{red} then find quadratures}

\subsubsection{Obtaining interpolation nodes}

The boundary $\Gamma$ is separated into a collection of intervals which are at least a fixed distance $\delta$  (measured in terms of arclength) away from a corner and the collection of intervals of length $2 \delta$ centered about each corner. The former are discretized using a standard smooth quadrature rule such as nested Gauss-Legendre quadrature while the latter are discretized using a custom set of interpolation nodes constructed in the following way.

First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,40],$ $x \in [0,1]$ are discretized using nested Gauss-Legendre panels in $x$ and a single Gauss-Legendre panel in $\mu$. This creates a $N \times M$ matrix where $N$ denotes the number of spatial discretization points $r_i$ and $M$ denotes the number of $\mu_j$ chosen. $M$ and $N$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1]$ for any $\mu$ in the specified range. A singular value decomposition is then performed on the $N\times M$ matrix. Let $K$ denote the number of singular values greater than $\epsilon.$ The right singular vectors correspond to discretizations of an orthonormal set of functions $\phi_1,\dots,\phi_K$ such that $x^\mu$ is in the span of $\phi_1,\dots,\phi_K$ to within an accuracy of $\epsilon.$

Finally, a set of interpolation points $x_j,$ $j=1,\dots,K$ and quadrature weights $w_j,$ $j=1,\dots,K$ are chosen for $\phi_1,\dots,\phi_K$ such that the matrix $U_{ij} = \phi_i(x_j) \sqrt{w_j}$ is well-conditioned. In practice suitable interpolation points can be obtained by using the roots of $\phi_{K+1}$ and calculating the corresponding weights by solving a linear system. The corresponding discretization nodes and weights for the corner-containing intervals of $\Gamma$ are obtained by suitable translations and scalings of $\{x_j\}$ and $\{w_j\}.$

\subsubsection{Construction of quadrature rules}

Once the discretization has been constructed it is necessary to construct appropriate quadrature for the integrals appearing in equation (\ref{eqn_1std}). When $s_i$ and $t$ do not belong to the same corner panel (in particular when either is not itself contained in a corner panel) then the weights and nodes associated with the discretization can be used as the quadrature rule. When $s_i$ corresponds to a corner panel special care must be taken. Instead, using an algorithm for generating generalized Gaussian quadratures \cite{}, quadrature nodes are chosen which integrate
\begin{align}
\int_{0}^\delta k(t,s_j) \tilde{\phi}_j(t)\,{\rm d}t
\end{align} 
where $\tilde{\phi}_j$ is a suitably scaled and translated copy of the singular function obtained in the discretization step, and for ease of exposition we assume that the corner panel corresponds to $(-\delta,\delta)$ in the parametrization with $t=0$ corresponding to the corner itself. Moreover, in light of symmetry between the two legs of the wedge it suffices to design quadratures assuming  $s_j$ lies in the half of a corner panel parametrized by $(-\delta,0).$
\begin{remark1}
Due to scale invariance, it suffices to compute quadratures for 
\begin{align}
\int_{0}^1 k(t,-x_j) {\phi}_j(t)\,{\rm d}t,
\end{align} 
where $x_j$ was one of the original discretization nodes generated on the interval $[0,1].$
\end{remark1}
\begin{remark1}
By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{W}_{i,j}$ such that if $s_1,\dots,s_{2K}$ correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
\begin{align}
\left| \int_{-\delta}^\delta k(t,s_i) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{W}_{ij} \tilde{\phi}_{m}(t_j) \right| < \epsilon
\end{align}
for all $i=1,\dots,2K$ and $m=1,\dots,K.$
\end{remark1}

@@

\subsection{Discretization of the Neumann problem}
In principle a similar method could be employed to discretize the Neumann boundary integral equations. Unfortunately, the singular nature of the powers (the smallest in the expansion given in Theorem \ref{thm_cord} lies in the range $(-1/2,0)$) makes it difficult to produce universal discretizations and quadratures which work for large ranges of angles. When the above method is run on these problems, discretization nodes tend to accumulate close to the corner (within $10^{-14}$). Apart from posing certain numerical challenges, it also makes the task of finding suitable quadrature formulae difficult. Instead a different set of discretization nodes and a different set of quadrature nodes can be constructed for each angle, though this would significantly increase the precomputation cost.
